---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# riekelib

**Author:** [Mark Rieke](https://www.thedatadiary.net/about/)
**License:** [MIT](https://github.com/markjrieke/riekelib/blob/master/LICENSE.md)

This is a collection of functions I use regularly both in professional & personal projects. Formalizing in a development package helps speed up workflows without having to re-define functions in each project. If it makes sense, I may coalesce common functions into their own dedicated package, but this can be considered an ever-in-progress testing ground.

Others should note that this is intended primarily for use by me, and it may not be the most well-documented or error-resilient.

## Installation

If you'd like to use, this package can be installed with the [devtools](https://www.r-project.org/nosvn/pandoc/devtools.html) package:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("https://github.com/markjrieke/riekelib")
```

## Usage

There are currently three function groups in this package:

1. `stats_extensions.R` contains functions that provide an interface to the `stats` package; namely, adding confidence intervals to common distributions. 
2. `bound_transforms.R` contains functions that rescale values on a bound scale to an unbounded scale, and vice-versa.
3. `qualtrics_extensions.R` contains functions that build upon the `qualtRics` package, but would be unlikely to be accepted in a PR. 


